---
title: "Project1"
author: "Yan Wang"
date: "2023-09-09"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
library(here)
library(tidyverse)

# tests if a directory named "data" exists locally
if (!dir.exists(here("data"))) {
    dir.create(here("data"))
}

# saves data only once (not each time you knit a R Markdown)
if (!file.exists(here("data", "chocolate.RDS"))) {
    url_csv <- "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-18/chocolate.csv"
    chocolate <- readr::read_csv(url_csv)

    # save the file to RDS objects
    saveRDS(chocolate, file = here("data", "chocolate.RDS"))
}
chocolate <- readRDS(here("data", "chocolate.RDS"))
as_tibble(chocolate)
glimpse(chocolate)
```

## Part 1: Explore data
### 1

```{r}
library(dplyr)
library(ggplot2)
qplot(rating, data = chocolate)
qplot(rating, data = chocolate, bins = 10)
qplot(rating, data = chocolate, bins = 15)
qplot(rating, data = chocolate, bins = 20)
qplot(rating, data = chocolate, bins = 25)
```

#### Answer: When I change the number of bins from 10, to 15, 20, 25, and default (30), these bars become more separately and bin size becomes more narrower, which, in my opinion, would be helpful to identify the characteristics in the data. I picked 25 because it shows these bars clealry and at the same time, the distribution of data is also clealy displayed.

### 2
```{r}
counties <- group_by(chocolate, country_of_bean_origin)
tibble <- count(counties)
print(tibble)
```
#### Answer: There are total 62 countries where the beans originated from. The total reviews for each country of bean origin are displayed in the tibble above. For example, Australia has 3 reviews, Belize has 76 reviews, etc.

### 3
```{r}
ecuador <- filter(chocolate, country_of_bean_origin == "Ecuador")
ecuador1 <- data.frame(summarise(ecuador, mean = mean(rating), sd = sd(rating), total = n()))
ecuador1
```
#### Answer: The average rating scores, the total number of reviews, and the standard deviation of the rating scores are 3.16, 219, and 0.51 respectively.

### 4
```{r}
ecuadors <- group_by(ecuador, specific_bean_origin_or_bar_name)
ecuadorss <- data.frame(summarise(ecuadors, quality = mean(rating)))
arrange(ecuadorss, desc(quality))
```
#### Answer: Corona Arriba, Guayas, Porcelana, Sorotaima,Machiques,batch pcl001, Rio Peripa H., and Tangaramake the best chocolate with beans from Ecuador.

### 5
```{r}
country_rate <- group_by(chocolate, country_of_bean_origin)
country_rates <- data.frame(summarise(country_rate, rates = mean (rating)))
arrange(country_rates, desc(rates))
```
#### Answer: The top 3 countries with the highest ratings on average are Tobago, China, and Sao Tome & Principe.

### 6
```{r}
country_rate1 <- mutate(country_rate, n = n())
country_rate2 <- filter(country_rate1, n >= 10)
country_rate3 <- data.frame(summarise(country_rate2, rates3 = mean(rating)))
arrange(country_rate3, desc(rates3))
```
#### Answer: Solomon Islands, Congo, and Cuba have the highest ratings on average after removing countries of bean origins that have less than 10 reviews.

### 7
```{r}
library(dplyr)
library(tidyr)
library(lubridate)
country_rate4 <- filter(country_rate1, n >= 50) 
country_rate6 <- mutate(country_rate4, percentage = case_when(
  cocoa_percent < 60 ~ "<60%",
  cocoa_percent >= 60 & cocoa_percent < 70 ~ ">=60 to <70%", 
  cocoa_percent >= 70 & cocoa_percent < 90 ~ ">=70 to <90%",
  cocoa_percent >= 90 ~ ">=90%"
) )
library(forcats)
country_rate6$percentage <- fct_relevel(country_rate6$percentage, "<60%", ">=60 to <70%", ">=70 to <90%", ">=90%")
country_rate7 <- country_rate6[, c("percentage", setdiff(names(country_rate6), "percentage"))]
country_rate8 <- data.frame(arrange(country_rate7, percentage))
ggplot(country_rate8, aes(x = percentage, y = rating)) + geom_boxplot() + facet_wrap(~country_of_bean_origin)
```

#### Answer: From the boxplots displayed above, chocolate percentage within "60%~90%" seems most highly rated. Most countries agree with the rating.

## Part 2: Join two datasets together
```{r}
library(gapminder)
library(dplyr)
newdata <- gapminder
newdata1 <- select(newdata, 1:2)
newdata2 <- rename(newdata1, country_of_bean_origin = country)
chocolate1 <- left_join(x = chocolate, y = newdata2, by = "country_of_bean_origin")
chocolate2 <- group_by(chocolate1, country_of_bean_origin)
chocolate3 <- mutate(chocolate2, reviews = n())
chocolate4 <- filter(chocolate3, reviews >= 10)
chocolate5 <- subset(chocolate4, country_of_bean_origin!="Blend")
chocolate6 <- chocolate5[is.na(chocolate5$continent),] %>%
mutate(continent = case_when(
      country_of_bean_origin %in% c('Fiji', 'Papua New Guinea', 'Sao Tome') ~ 'Oceania',
      country_of_bean_origin %in% c('Congo', 'Solomon Islands') ~ 'Africa',
      country_of_bean_origin %in% c('Vanuatu') ~ 'Europe',
      country_of_bean_origin %in% c('Trinidad', 'Grenada', 'St. Lucia') ~ 'Europe',
      country_of_bean_origin %in% c('U.S.A.', 'Belize') ~ 'Americas'))
ggplot(chocolate6, aes(x = continent, y = rating)) + geom_violin() + labs(x= "continents", y = "ratings")
```

## Part 3: Convert wide data into long data
```{r}
library(dplyr)
library(tidyr)
newchocolate <- chocolate %>% mutate(beans = case_when(grepl("B", ingredients) ~ 1, TRUE ~ 0)) %>% mutate(sugar = case_when(grepl("S", ingredients) ~ 1, TRUE ~ 0)) %>% mutate(cocoa_butter = case_when(grepl("C", ingredients) ~ 1, TRUE ~ 0)) %>% mutate(vanilla = case_when(grepl("V", ingredients) ~ 1, TRUE ~ 0)) %>% mutate(letchin = case_when(grepl("L", ingredients) ~ 1, TRUE ~ 0)) %>% mutate(salt = case_when(grepl("Sa", ingredients) ~ 1, TRUE ~ 0))
library(stringr)
newchocolate1 <- newchocolate %>% mutate(char_cocoa = case_when(str_detect(most_memorable_characteristics, "cocoa") ~1, TRUE ~ 0)) %>% mutate(char_sweet = case_when(str_detect(most_memorable_characteristics, "sweet") ~1, TRUE ~ 0)) %>% mutate(char_nutty = case_when(str_detect(most_memorable_characteristics, "nutty") ~1, TRUE ~ 0)) %>% mutate(char_creamy = case_when(str_detect(most_memorable_characteristics, "creamy") ~1, TRUE ~ 0)) %>% mutate(char_roasty = case_when(str_detect(most_memorable_characteristics, "roasty") ~1, TRUE ~ 0)) %>% mutate(char_earthy = case_when(str_detect(most_memorable_characteristics, "earthy") ~1, TRUE ~ 0))
newchocolate2 <- group_by(newchocolate1, review_date)
newchocolate3 <- data.frame(summarise(newchocolate2, beansm = mean(beans), sugarm = mean(sugar), cocoa_butterm = (cocoa_butter), vanillam = mean(vanilla), letchinm = mean(letchin), saltm = mean(salt), char_cocoam = mean(char_cocoa), char_sweetm = mean(char_sweet), char_nuttym = mean(char_nutty), char_creamym = mean(char_creamy), char_roastym = mean(char_roasty), char_earthym = mean(char_earthy)))
newchocolate3 %>% pivot_longer(-review_date, names_to = "feature", values_to = "mean_score")
newchocolate4 <- tibble(newchocolate3 %>% pivot_longer(-review_date, names_to = "feature", values_to = "mean_score"))
print(newchocolate4)
```
### Part 4: Data visualization
```{r}
library(ggplot2)
ggplot(newchocolate4, aes(x = review_date, y = mean_score, color = feature)) + geom_point(size = 1) + geom_smooth(method = "loess", formula = "y~x") + labs(title = "Mean Scores Trends Over Time", subtitle = "The mean scores of letchinm and vanillam decreasing over time, others maintaining stable", caption = "Yan Wang", x= "Review date", y = "Mean score") + theme_minimal() + theme(plot.background = element_rect(fill = "#FFEBCD"), panel.background = element_rect(fill = "white"), panel.grid.major = element_line(color = "#FFFAF0"), plot.title = element_text(size = 16, face = "bold"),plot.subtitle = element_text(size = 11, face = "italic"), legend.position = "right", legend.text = element_text(size = 8), legend.title = element_text(size = 10)) 

```

### Part 5: Make the worst plot you can!
```{r}
chocolate %>% ggplot(aes(x = as.factor(country_of_bean_origin), y = rating))
chocolate %>% ggplot(aes(x = as.factor(country_of_bean_origin), y = rating)) + geom_violin()
chocolate %>% ggplot(aes(x = as.factor(country_of_bean_origin), y = cocoa_percent))
qplot(rating, data = chocolate, fill = country_of_bean_origin, binwidth = 2)
qplot(review_date, cocoa_percent, data = chocolate, color = country_of_bean_origin)
qplot(review_date, rating, data = chocolate, geom = c("smooth"))
qplot(country_of_bean_origin, rating, data = chocolate, geom = "boxplot")
```


#### Answer:
##### 1. It suggests that points should be displayed clearly and easy to understand at a glance. Clutter should be avoided.  
##### 2. It suggests that I should choose the right type of graphs to best represent the data.
##### 3. It suggests that I should design the x-axis and y-axis properly.
##### 4. It suggests that I should focus on visualizing the most meaningful aspects of the data.
##### 5. It suggests that removing any unnecessary elements is important.
##### 6. It suggests that providing clear labels for axes, data points, title, etc are important and meaningful.
##### 7. It suggests that choosing the proper graphs and showing the most relevent information of the data is necessary.

### Part 6: Make my plot a better plot!
```{r}
remotes::install_github("MatthewBJane/theme_park")
glimpse(newchocolate4)
newchocolate4 %>% ggplot(aes(x = review_date, y = mean_score, fill = feature)) + geom_violin()
newchocolate4 %>% ggplot(aes(x = review_date, y = mean_score, colour = feature)) + geom_point() + theme_minimal() + theme(plot.background = element_rect(fill = "#FFdBCD"), panel.background = element_rect(fill = "white"), panel.grid.major = element_line(color = "#FFaAF0"))
newchocolate4 %>% ggplot(aes(mean_score, colour = feature)) + geom_histogram() + labs(title = "Mean Scores of different features", subtitle = "Most features falling in lower socres", x= "Mean scores")
newchocolate4 %>% ggplot(aes(x = review_date, y = mean_score, colour = feature)) + geom_point() + facet_wrap(~feature)
newchocolate4 %>% ggplot(aes(mean_score, colour = feature)) + geom_freqpoly() + facet_wrap(~feature)
chocolate6 %>% ggplot(aes(x = continent, y = rating, colour = continent)) + geom_boxplot() + theme_minimal() + ThemePark::theme_oppenheimer()
chocolate6 %>% ggplot(aes(x = continent, y = rating, colour = continent)) + geom_jitter() + ThemePark::theme_barbie()

```

#### Answer:
##### 1. I fill each "violin" with different colors, making the graph visually appealing and meaningful.
##### 2. I change the theme by increasing the panel background, plot background, and panel grid, which makes it more beautiful.
##### 3. I add the title, subtitle, and x axis labers, making it more clear to understand.
##### 4. I make the graph divided into 12 panels according to features, making it easier to find the different tendencies over time between different features.
##### 5. I choose using "geom_freqpoly()" to show the characteristics of the data, which makes it more obvious. 
##### 6. I choose using "boxplot" to show the characteristics of data, making it more easier to compare the distribution between different continents. Also, I use the "oppenheimer" theme to make it look cool.
##### 7. I change the theme to "Barbie them", and change the typer of graph. Compared to boxplot, "jitter" could show individual values, which is useful when I focus on the individual values, rather than group values.


